\bf Interactive Visualization of Hierarchically Structured Data

### 2017-07-11 reviewer_response.tex

\textit{This small sampling of a large body of work points to the need for a
  cleaner conceptualization and clarifications of the contribution of the work
  presented in this paper relative to prior efforts.}

We have have modified our literature review to begin with a broader discussion
of tree and time series visualization methods, before proceeding to those
methods used more directly in our work. Further, we have added a bullet list
describing more concretely the contributions of this paper within the broader
body of knowledge.

\textit{My main concern regarding the presentation of the work lies in the third
  and fourth views - why are they presented as distinct? It would seem to me
  that all of the described functionality could be configured in that one view.
  In fact, I could imagine including the DOi in the same view as well - why are
  multiple views needed?}

The idea of combining these displays is interesting, and we have attempted to
implement a version which would highlight the series / nodes that lay in both
(1) the union of all treeboxes and (2) the intersection of all timeboxes.
However, we found this idea difficult to implement, for technical rather than
conceptual reasons -- when attempting to have both brush interactions for
querying and mouseover interactions for providing detail, the events conflict.
Indeed, we implemented the first and third recommendations described in
\href{https://github.com/d3/d3/issues/1604}{this d3 issue}, but in both cases we
found it necessary to introduce a lag between mousedown and the start of
brushing in order for the event to properly register. This lag created a drag on
responsiveness, and the value gained by unifying the displays did not seem worth
the cost of less fluid interactivity.

### 2017-07-11 treelapse.tex
fix the section labeling

\subsection*{Introduction}\label{introduction}

@@

\subsubsection*{Problem Motivation}\label{problem-motivation}

@@

\subsubsection*{Problem Abstraction}\label{problem-abstraction}

@@

\subsection*{Background Literature and Solution
Principles}\label{background-literature-and-solution-principles}

@@

\subsection*{Specific Proposals}\label{specific-proposals}

@@

\subsection*{Case Studies}\label{case-studies}

@@

\subsubsection*{Bacterial Dynamics of Antibiotics Time
Courses}\label{bacterial-dynamics-of-antibiotics-time-courses}

@@

\subsubsection*{Differential Bacterial Abundance and Preterm
Births}\label{differential-bacterial-abundance-and-preterm-births}

@@

\subsubsection*{Dynamics in Housing Prices}\label{zillow-study}

@@

\subsubsection*{Sources of Variation in Bikesharing
Demand}\label{bikesharing-study}

@@

\subsubsection*{Hierarchically Clustering the Global Patterns Data}\label{global_patterns}

@@

\subsubsection*{Inspecting Confirmatory Analysis}\label{structssi}

@@

\subsection*{Conclusion and Future Work}\label{conclusion}

>>>>

\section{Introduction}\label{introduction}

@@

\subsection{Problem Motivation}\label{problem-motivation}

@@

\subsection{Problem Abstraction}\label{problem-abstraction}

@@

\subsection{Background Literature and Solution
Principles}\label{background-literature-and-solution-principles}

@@

\subsection{Specific Proposals}\label{specific-proposals}

@@

\section{Case Studies}\label{case-studies}

@@

\subsection{Bacterial Dynamics of Antibiotics Time
Courses}\label{bacterial-dynamics-of-antibiotics-time-courses}

@@

\subsection{Differential Bacterial Abundance and Preterm
Births}\label{differential-bacterial-abundance-and-preterm-births}

@@

\subsection{Dynamics in Housing Prices}\label{zillow-study}

@@

\subsection{Sources of Variation in Bikesharing
Demand}\label{bikesharing-study}

@@

\subsection{Hierarchically Clustering the Global Patterns Data}\label{global_patterns}

@@

\subsection{Inspecting Confirmatory Analysis}\label{structssi}

@@

\section{Conclusion and Future Work}\label{conclusion}
